An open-source integrated framework for the automation of citation collection and screening in systematic reviews.

### 2021-12-23 Manuscript/Manuscript.tex
small edits to Results table
updated front page

\title{Main manuscript}

\author{
    David S. Hippocampus
    \thanks{Use footnote for providing further information about author
(webpage, alternative address)---\emph{not} for acknowledging funding
agencies. Optional.}
   \\
    Department of Computer Science \\
    Cranberry-Lemon University \\
  Pittsburgh, PA 15213 \\
  \texttt{\href{mailto:hippo@cs.cranberry-lemon.edu}{\nolinkurl{hippo@cs.cranberry-lemon.edu}}} \\
   \And
    Elias D. Striatum
   \\
    Department of Electrical Engineering \\
    Mount-Sheikh University \\
  Santa Narimana, Levand \\
  \texttt{\href{mailto:stariate@ee.mount-sheikh.edu}{\nolinkurl{stariate@ee.mount-sheikh.edu}}} \\
  }

@@

\begin{abstract}
Enter the text of your abstract here.
\end{abstract}

\keywords{
    blah
   \and
    blee
   \and
    bloo
   \and
    these are optional and can be removed
  }

@@

To evaluate the hyperparameter effect of performance, we set up a ``grid
search'' (Claesen and De Moor 2015; L. Yang and Shami 2020) on a
prelabelled ``validation set'' made of the first 1200 records from the
first session data set. The framework tested each hyperparameter
combination until four CR iterations with no positive records were
returned or the whole data set got labelled.\\
For each combination, a performance score was computed as the product of
``Efficiency'' (1 minus the ratio of records that required review over
the total) and ``Sensitivity'' (number of positive records found over
the total of positives). We then identified homogeneous ``performance
clusters'' of scores given hyperparameter values using a partition tree
(Therneau and Atkinson 2019). For the rest of the study, we used the
best hyperparameter set in terms of Sensitivity followed by Efficiency
from the cluster with the highest average score.

@@

The first search session returned a total of 27600 unique records,
specifically 12719 (71.6\% of the total) records from the EMBASE
database, followed by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from
SCOPUS, 2100 (11.8\%) from WOS, and 60 (0.34\%) from IEEE (Table 1).
There were various degrees of overlapping between sources, with the
38.4\% of records being present in more than one database and EMBASE and
IEEE being the databases with the higher uniqueness ratios. The final
data set was composed by 17755 unique records.\\
The first 250 records (based on ``simple query ordering'') were manually
labeled. Of these 43 (17.2\%) were labeled as positive, and 207 (82.8\%)
as negative.

@@

\caption{\label{tab:Table 1}\textbf{Table 1}. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. All session shows records after joining and deduplication of the Session 1 and Session 2 data set.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlrl}
\toprule
Session & Source & Records & \% over total & Source specific records & \% over source total\\
\midrule
\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
 & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
\addlinespace
 & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
 & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
 & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
\addlinespace
 & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
 & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
\bottomrule
\end{tabular}}
\end{table}

Records were joined into a database and arrange by simple query
ordering; of these, the first 250 records were labelled to create the
initial training set.\\
Using the classification model,7 automatic classification and manual
review iterations (CR) were performed (Table 2). It is possible to
observe how the number of records that required manual review dropped
rapidly between iterations, indicating that the engine was converging
while the uncertainties were resolved.\\
This phenomenon is better depicted in Fig. 1 of the Supplemental
Material S2. It shows the mixture distribution of the PPD of the
records, specifically for the reviewed positive and negative records,
and for records that need manual review after the classification step:
it can be noticed how the distribution of the uncertain records shrinks
(they concentrate in a shorter probability range) and shifts toward the
negative zone as more positive matches are found and reviewed.
Accordingly (Table 2), the number of new positives found drops after the
first couple of iterations. As per default, the classification process
was stopped after four rounds with no new positive matches; a total
number of 101 positives were found over 766 manually reviewed records
(13.2\% positivity rate).\\

@@

By evaluating how often a term was used by the classification model, it
is possible to define their relevance in labeling the records (see
Methods). Here follows the 15 most relevant terms by inclusion rate over
10,000 posterior tree, described as: Term (citation part): Inclusion
Rate (Inclusion Stability) {[}linear Relative Risk, Statistic{]}.

@@

The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
documents.\\
The engine was able to pick up the central concept of the research,
i.e., ``patient transport'' or ``transfer'' through a ``network'' of
``facility''ies that facilitates the ``spread'' of infections, and even
one of the authors of this study (Donker T.) as well as the region of
interest (``Orange County'') of another research group active on the
topic of healthcare asociated pathogen spreading over hospital networks.
It is interesting to see that some terms were considered highly relevant
for the BART models (e.g., ``Worker'' in 6th position out of more than
3800 terms considered) although in a simpler linear model their effect
would be hardly significant (statistic: -1.21 s.e.); these are terms
which are relevant only together with other terms but not by themselves,
highlighting the extra predictive power brought by a non-linear model
like BART.\\
A more extensive set of terms is presented in Table 1 of Supplemental
Material S2.

@@

Six CR rounds were necessary to complete the second session
classification, with just 6 new positive found after reviewing 568 extra
records. The first CR iteration required the user to review a
substantial number of records (1,273), but just labelling 275 of them
(the canonical 250 plus 25 that were already labelled during the
framework hyperparameter tuning) was sufficient to drop this number to
just 190 in the subsequent round. An evaluation of the convergence
(Figure 1, Supplemental Material S2) showed that, in addition to the
dynamics already observed in session 1 (shrinkage and negative shift), a
second mode appeared in the mixture distribution of the records to be
reviewed, centred in a highly positive zone. The interpretation is that
as the number of negative training records increases, the engine gets
more and more skeptical and asks to review even some records labelled as
positive in the initial training set in Session 1. This behaviour can be
useful to spot classification errors and inconsistencies. Considering
both sessions, 1333 records were reviewed and 107 (8.03\%) were found.

@@

Table 3 shows various performance indexes for both sessions, both
descriptive (Total records, Reviewed records, Observed positive matches)
and estimated through the surrogate model (Expected efficiency,
Predicted positive matches, Expected sensitivity, \(R^2\)).\\
In session 1 we observe an expected total number of positives of 101
{[}101, 108{]} for an estimated sensitivity of 100\% {[}93.5\%, 100\%{]}
and efficiency of 95.7\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
a drop in the expected sensitivity, especially in the lower margin
(97.3\% {[}73.8\%, 100\%{]}), due to the fact that as the number of
records grows, even a small probability can translate, in the worst case
scenario, into a relevant number of missed positive matches (145 in this
case). To ascertain that no evident positives were missed, we evaluated
100 more records between the unreviewed ones with the highest median
predicted probability produced by the engine and found no additional
positive matches.

@@

\caption{\label{tab:Table 3}\textbf{Table 3}. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90\% PrI truncated to the observed realization in the dataset [trunc. PrI] (see. methods). Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported. PrI: Predictive Intervals; CrI: Credibility Intervals}
\centering
\begin{tabular}[t]{lll}
\toprule
Indicator & Session 1 & Session 2\\
\midrule
\cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{98371}\\
Reviewed records (\% over total records) & 761 (4.29\%) & 1316 (1.34\%)\\
\cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.7\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.2\%, 98.7\%]}\\
Observed positive matches (\% over total records) & 101 (0.57\%) & 107 (0.11\%)\\
\cellcolor{gray!6}{Predicted positive matches [trunc. 90\% PrI]} & \cellcolor{gray!6}{101 [101, 108]} & \cellcolor{gray!6}{110 [107, 145]}\\
\addlinespace
Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [73.8\%, 100\%]\\
\cellcolor{gray!6}{Simple Model $R^2$ [90\% CrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
\bottomrule
\end{tabular}
\end{table}

@@

We propose a new integrated framework to help researchers collect and
screen scientific publications characterised by high performance and
versatility, joining the growing field of systematic review automation
(SRA) and helpers (SRH) tools (A. M. Cohen et al. 2006, 2010; Ananiadou
et al. 2009; O'Mara-Eves et al. 2015). This framework joins standard
approaches and uses ad-hoc solutions to deal with common SRA issues. By
freely sharing the tool as an open-source R package and by following a
modular design, we tried to adopt some of the so-called Vienna
Principles advocated by the International Collaboration for the
Automation of Systematic Reviews (ICASR) (E. Beller et al. 2018).\\
The framework consists of four main components: 1) an integrated
query-based citation search and management engine, 2) a text-to-feature
extractor module, 3) a Bayesian active machine learning-based citation
classifier, and 4) a data-driven search query generation algorithm.\\

The framework's search engine module is capable of automatically
collecting citation data from three well-known scientific databases
(i.e.~Pubmed, Web of Science, and the database of the Institute of
Electrical and Electronics Engineers) as well as process manually
downloaded results from both the mentioned and other (SCOPUS, EMBASE)
databases. In comparison, most SRH tools, commercial or free to use,
rely either on internal databases (e.g., Mendeley
\url{https://www.mendeley.com/}) sometimes focusing just on a particular
topic (Visser 2010) or on a single external data source (Thomas and
Brunton 2007; Poulter et al. 2008; Soto, Przybyła, and Ananiadou
2019).\\
Mixing different databases is fundamental to have a more comprehensive
view of the literature (Bajpai et al. 2011; Wilkins, Gillies, and Davies
2005; Woods and Trewheellar 1998): in our results, 18.7\% of the
positive matches found were unique for one of the different data
sources, and no positive record was present in all of them (data not
shown).\\
The online search algorithms are efficient enough to manage tens of
thousands of search results, using various expedients to overcome the
limitations of the queried databases in terms of traffic and download
quota. The results are then automatically organized, deduplicated and
arranged by ``simple query ordering'' in a uniform corpus. The
preliminary ordering allow to increase the positivity rate in the
initial training set (Wallace, Small, et al. 2010).

The feature extractor module uses modern NLP techniques (Ananiadou and
McNaught 2006; K. B. Cohen and Hunter 2008) to transform text into input
data for machine learning. We did not include classical n-grams
(Schonlau and Guenther 2017), but we used network analysis to find
non-consecutive frequently associated terms, a generalisation of n-grams
relaxing the term adjacency assumption. A similar network approach was
applied to merge redundant terms to make model estimation more efficient
and reduce noise.\\
The use of concurrency network-driven modelling of text is not new
(Francois Rousseau 2015; Violos et al. 2016; François Rousseau, Kiagias,
and Vazirgiannis 2015; Ohsawa, Benson, and Yachida 1998) and is a
valuable tool to extract semantic information not evident in one-word or
consecutive n-gram models.\\

The framework's record classification module implements an active
machine learning approach Miwa et al. (2014) and is based on Bayesian
Additive Regression Trees (BART) (Chipman et al. 2010; Kapelner and
Bleich 2013). When implementing our algorithm we adopted best practices
from other SRA studies, bringing improvements at various levels.\\
As with other boosted trees algorithms (Hastie, Tibshirani, and Friedman
2009), BART can explore complex non-linearities, perform variable
selection, manage missing data while sporting high performance in
predictive power.\\
However, its Bayesian foundation provides further benefits: less
sensitivity on hyperparameter choices, natural regularisation through
priors, and, especially, predictive distributions as output in place of
point-wise predictions (Soria-Olivas et al. 2011; Joo, Chung, and Seo
2020; Jospin et al. 2020). By selecting relatively tight prior
distributions, we discouraged excessively deep trees, long sequences of
trees, or extreme predicted probabilities, to decrease the risk of
overfitting.\\
The algorithm runs multiple replications of the model and averages their
predictive distributions creating an ``ensemble''; this technique has
been shown to improve out-of-sample predictive performance (Zhou 2021;
Dietterich 2000), as we were able to confirm during the hyperparameter
evaluation (Supplemental Material S2). Ensembling reduces the
uncertainty in the predictive distribution tails related to the
randomness in the MCMC fit (Robert, Casella, and Casella 2004),
generating a shift of probability mass towards the distribution centre
and stabilising it (i.e., decreasing variance without impacting bias).
On the other hand, just imposing robust uninformative priors against
extreme predictions would have decreased variance but also shifted the
distribution towards a non-decision zone, increasing bias (Hansen et al.
2000).\\
Since the number of model replications significantly impacts computation
times, we decided to use ten replicas, the lower value after which
showed performance stabilisation during the hyperparameter evaluation.\\
We also investigated whether bootstrapping between replications (Breiman
1996) would improve performance, but, contrary to theory (Díez-Pastor et
al. 2015), it was demonstrated to be slightly detrimental (Supplemental
Material S2) compared to simple ensembling.\\

@@

The field of literature review automation is maturing rapidly, and we
expect an increasing use of such technologies to manage the ever-faster
rate of scientific production. We believe it is appreciable that a
multiplicity of tools are being made available to let researchers and
policymakers find the instrument that better fits their needs.\\
We contribute to this field with an innovative framework that provide
excellent performance and easy integration with existing systematic
review pipelines. The value of this work lies not only in the framework
itself, which we provide as open-source software, but in the set of
methodologies we developed to solve various SRA issues and that can be
used to improve already existing solutions.

>>>>

\title{An open-source integrated framework for the automation of
citation collection and screening in systematic reviews.}

\author{
    Angelo D'Ambrosio
   \\
    Institute for Infection Prevention and Hospital Hygiene \\
    Freiburg University Hospital \\
  Freiburg, Germany \\
  \texttt{\href{mailto:angelo.d.ambrosio@uniklinik-freiburg.de}{\nolinkurl{angelo.d.ambrosio@uniklinik-freiburg.de}};
\href{mailto:a.dambrosioMD@gmail.com}{\nolinkurl{a.dambrosioMD@gmail.com}}} \\
   \And
    Tjibbe Donker
   \\
    Institute for Infection Prevention and Hospital Hygiene \\
    Freiburg University Hospital \\
  Freiburg, Germany \\
  \texttt{\href{mailto:tjibbe.donker@uniklinik-freiburg.de}{\nolinkurl{tjibbe.donker@uniklinik-freiburg.de}}} \\
   \And
    Hajo Grundmann
   \\
    Institute for Infection Prevention and Hospital Hygiene \\
    Freiburg University Hospital \\
  Freiburg, Germany \\
  \texttt{\href{mailto:hajo.grundmann@uniklinik-freiburg.de}{\nolinkurl{hajo.grundmann@uniklinik-freiburg.de}}} \\
  }

@@

\begin{abstract}
The exponential growth in scientific production makes its summarisation
through secondary literature exceedingly demanding in terms of time and
human resources. We introduce a new open-source framework that
significantly increases efficiency during the citation collection and
screening phases of systematic reviews.\\
The framework introduces three main tools: 1) an automatic citation
search engine and manager that allows collecting records from multiple
citation databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified
query syntax; 2) a citation screening tool based on Bayesian active
machine learning and natural language processing, which requires users
feedback only on uncertain classifications to increase predictive
accuracy iteratively; 3) a semi-automatic data-driven query generator to
create new search queries from existing reviewed citation data sets.\\
The framework was applied on an example topic performing citation
collection and screening. We estimated median posterior Sensitivity and
Efficiency {[}90\% Credible Intervals{]} using Bayesian simulation to
predict the distribution of possibly missed relevant matches in the
unreviewed records.\\
17755 unique records were collected through the framework citation
manager; 101 over 766 records were found to be relevant after manual
evaluation, while the rest were excluded by the automatic
classification; the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]}
for a Sensitivity of 100\% {[}93.5\%, 100\%{]}. A new search query was
generated from the labelled dataset, and 82579 more records were
collected. Only 567 records required human review after the automatic
screening, and six additional positive matches were found. Including the
additional records, the overall expected Sensitivity dropped to 97.3\%
{[}73.8\%, 100\%{]} while the Efficiency raised to 98.6\% {[}98.2\%,
98.7\%{]}.\\
The framework can significantly reduce human resources requirements for
systematic reviews by simplifying citation collection and screening
while demonstrating exceptional sensitivity even on large data sets.
\end{abstract}

\keywords{
    Systematic review automation
   \and
    Citation management
   \and
    Online data collection
   \and
    Active machine learning
   \and
    Natural language processing
   \and
    Bayesian modeling
  }

@@

To evaluate the hyperparameter effect of performance, we set up a ``grid
search'' (Claesen and De Moor 2015; L. Yang and Shami 2020) on a
prelabelled ``validation set'' made of the first 1200 records from the
first session data set. The framework tested each hyperparameter
combination until four CR iterations with no positive records were
returned or the whole data set got labelled.\\
For each combination, a performance score was computed as the product of
``Efficiency'' (1 minus the ratio of records that required review over
the total) and ``Sensitivity'' (number of positive records found over
the total of positives). We then identified homogeneous ``performance
clusters'' of scores given hyperparameter values using a partition tree
(Therneau and Atkinson 2019). For the rest of the study, we used the
best hyperparameter set in terms of Sensitivity followed by Efficiency
from the cluster with the highest average score.\\

@@

The first search session returned a total of 27600 records, specifically
12719 (71.6\% of the total) records from the EMBASE database, followed
by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from SCOPUS, 2100 (11.8\%)
from WOS, and 60 (0.34\%) from IEEE (Table 1). There were various
degrees of overlapping between sources, with the 38.4\% of records being
present in more than one database and EMBASE and IEEE being the
databases with the higher uniqueness ratios. The final data set was
composed by 17755 unique records.\\
The first 250 records (based on ``simple query ordering'') were manually
labeled. Of these 43 (17.2\%) were labeled as positive, and 207 (82.8\%)
as negative.

@@

\caption{\label{tab:Table 1}\textbf{Table 1}. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates), and number or records specific for a source as absolute value and as percentage over the source total. All session shows records after joining and deduplication of the Session 1 and Session 2 data set.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlrl}
\toprule
Session & Source & Records & \% over total & Source specific records & \% over source total\\
\midrule
\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
 & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
\addlinespace
 & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
 & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
 & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
\addlinespace
 & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
 & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
\bottomrule
\end{tabular}}
\end{table}

The labeled records were used to train the Bayesian classification model
used to label the remaining records. After seven classification and
review (CR) iterations (three resulting in new positive matches and four
extra replications to account for stochastic variability), a total of
101 positives matches were found, requiring manual review of 766 records
(13.2\% positivity rate).\\
It is possible to observe how the number of records that required manual
review dropped rapidly between iterations (Table 2), indicating that the
engine was converging while the uncertainties were resolved.\\
This phenomenon is better depicted in Fig. 1 of the Supplemental
Material S2, showing the mixture distribution of the PPDs of the
records, specifically for the reviewed positive and negative records,
and for records that need manual review after the classification step:
it can be noticed how the distribution of the uncertain records shrinked
(they concentrate in a shorter probability range) and shifted toward the
negative zone as more positive matches are found and reviewed.

@@

We extracted the 15 term more relevant for the classification model,
described as: Term (citation part): Inclusion Rate (Inclusion Stability)
{[}linear Relative Risk, Statistic{]}.

@@

The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
documents.\\
The engine was able to pick up the central concept of the research,
i.e., ``patient transport'' or ``transfer'' through a ``network'' of
``facility''ies that facilitates the ``spread'' of infections, and even
one of the authors of this study (Donker T.) as well as the region of
interest (``Orange County'') of another research group active on the
topic of healthcare asociated pathogen spreading over hospital networks.
Some terms were considered highly relevant for the BART models (e.g.,
``Worker'' in 6th position out of more than 3800 terms considered)
although in a simpler linear model their effect would be hardly
significant (statistic: -1.21 s.e.); these are terms which are relevant
only in conjunction with other terms but not by themselves, highlighting
the extra predictive power brought by a non-linear model like BART.\\
A more extensive set of terms is presented in Table 1 of Supplemental
Material S2.

@@

Six CR rounds were necessary to complete the second session
classification, with just 6 new positive found after reviewing 568 extra
records. The first CR iteration required the user to review a
substantial number of records (1,273), but just labelling 275 of them
(the canonical 250 plus 25 that were already labelled during the
framework hyperparameter tuning) was sufficient to drop this number to
just 190 in the subsequent round. An evaluation of the convergence
(Figure 1, Supplemental Material S2) showed that, in addition to the
dynamics already observed in session 1 (shrinkage and negative shift), a
second mode appeared in the mixture distribution of the records to be
reviewed, centred in a highly positive zone. The interpretation is that
as the number of negative training records increases, the engine gets
more and more skeptical and asks to review even some records labelled as
positive in the initial training set generated during Session 1. This
behaviour can be useful to spot classification errors and
inconsistencies. Considering both sessions, 1333 records were reviewed
and 107 (8.03\%) were found.

@@

Table 3 shows various performance indexes for both sessions, both
descriptive (Total records, Reviewed records, Observed positive matches)
and estimated through the surrogate model (Expected efficiency,
Predicted positive matches, Expected sensitivity, \(R^2\)).\\
In session 1 we observe an expected total number of positives of 101
{[}101, 108{]} for an estimated sensitivity of 100\% {[}93.5\%, 100\%{]}
and efficiency of 95.7\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
a drop in the expected sensitivity, especially in the lower margin
(97.3\% {[}73.8\%, 100\%{]}), due to the fact that as the number of
records grows, even a small probability can translate, in the worst case
scenario, into a relevant number of missed positive matches (145 in this
case). To ascertain that no evident positives were missed, we evaluated
100 more records between the unreviewed ones with the highest median
predicted probability produced by the engine and found no additional
positive matches.\\

@@

\caption{\label{tab:Table 3}\textbf{Table 3}. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90\% PrI truncated to the observed realization in the dataset [trunc. PrI] (see. methods). Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported. PrI: Predictive Intervals; CrI: Credibility Intervals.}
\centering
\begin{tabular}[t]{lll}
\toprule
Indicator & Session 1 & Session 2\\
\midrule
\cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{98371}\\
Reviewed records (\% over total records) & 761 (4.29\%) & 1316 (1.34\%)\\
\cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.7\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.2\%, 98.7\%]}\\
Observed positive matches (\% over total records) & 101 (0.57\%) & 107 (0.11\%)\\
\cellcolor{gray!6}{Predicted positive matches [trunc. 90\% PrI]} & \cellcolor{gray!6}{101 [101, 108]} & \cellcolor{gray!6}{110 [107, 145]}\\
\addlinespace
Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [73.8\%, 100\%]\\
\cellcolor{gray!6}{Simple Model $R^2$ [90\% CrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
\bottomrule
\end{tabular}
\end{table}

@@

We propose a new integrated framework to help researchers collect and
screen scientific publications characterised by high performance and
versatility, joining the growing field of systematic review automation
(SRA) and helpers (SRH) tools (A. M. Cohen et al. 2006, 2010; Ananiadou
et al. 2009; O'Mara-Eves et al. 2015). This framework joins standard
approaches and uses ad-hoc solutions to deal with common SRA issues. By
freely sharing the tool as an open-source R package and by following a
modular design, we tried to adopt some of the so-called Vienna
Principles advocated by the International Collaboration for the
Automation of Systematic Reviews (ICASR) (E. Beller et al. 2018).\\
The framework consists of four main components: 1) an integrated
query-based citation search and management engine, 2) a Bayesian active
machine learning-based citation classifier, and 3) a data-driven search
query generation algorithm.\\

The framework's search engine module is capable of automatically
collecting citation data from three well-known scientific databases
(i.e., Pubmed, Web of Science, and the database of the Institute of
Electrical and Electronics Engineers) as well as process manually
downloaded results from both the mentioned and other (SCOPUS, EMBASE)
databases. In comparison, most SRH tools, commercial or free to use,
rely either on internal databases (e.g., Mendeley
\url{https://www.mendeley.com/}) sometimes focusing just on a particular
topic (Visser 2010) or on a single external data source (Thomas and
Brunton 2007; Poulter et al. 2008; Soto, Przybyła, and Ananiadou
2019).\\
Mixing different databases is fundamental to have a more comprehensive
view of the literature (Bajpai et al. 2011; Wilkins, Gillies, and Davies
2005; Woods and Trewheellar 1998): in our results, 18.7\% of the
positive matches found were unique for one of the different data
sources, and no positive record was present in all of them (data not
shown).\\
The online search algorithms are efficient enough to manage tens of
thousands of search results, using various expedients to overcome the
limitations of the queried databases in terms of traffic and download
quota. The results are then automatically organized, deduplicated and
arranged by ``simple query ordering'' in a uniform corpus. The
preliminary ordering allow to increase the positivity rate in the
initial training set (Wallace, Small, et al. 2010).\\

For the framework's record classification module we employed an active
machine learning approach Miwa et al. (2014) based on the best practices
from other SRA studies, bringing further improvements at various
levels.\\
The feature extractor module uses modern NLP techniques (Ananiadou and
McNaught 2006; K. B. Cohen and Hunter 2008) to transform text into input
data for machine learning. We did not include classical n-grams
(Schonlau and Guenther 2017), but we used network analysis to find
non-consecutive frequently associated terms, a generalisation of n-grams
relaxing the term adjacency assumption. This approach allows also to
find term connections across fields, for example a term having a
different relevancy if associated with a specific author. The same
technique but with different parameters was applied to merge redundant
terms to make model estimation more efficient and reduce noise.\\
The use of concurrency network-driven modelling of text is not new
(Francois Rousseau 2015; Violos et al. 2016; François Rousseau, Kiagias,
and Vazirgiannis 2015; Ohsawa, Benson, and Yachida 1998) and is a
valuable tool to extract semantic information not evident in one-word or
consecutive n-gram models.\\

The automatic classification algorithm is based on Bayesian Additive
Regression Trees (BART) (Chipman et al. 2010; Kapelner and Bleich 2013).
As with other boosted trees algorithms (Hastie, Tibshirani, and Friedman
2009), BART can explore complex non-linearities, perform variable
selection, manage missing data while sporting high performance in
predictive power.\\
However, its Bayesian foundation provides further benefits: less
sensitivity on hyperparameter choices, natural regularisation through
priors, and, especially, predictive distributions as output in place of
point-wise predictions (Soria-Olivas et al. 2011; Joo, Chung, and Seo
2020; Jospin et al. 2020). By selecting relatively tight prior
distributions, we discouraged excessively deep trees, long sequences of
trees, or extreme predicted probabilities, to decrease the risk of
overfitting.\\
The algorithm runs multiple replications of the model and averages their
predictive distributions creating an ``ensemble''; this technique has
been shown to improve out-of-sample predictive performance (Zhou 2021;
Dietterich 2000), as we were able to confirm during the hyperparameter
evaluation (Supplemental Material S2). Ensembling reduces the
uncertainty in the predictive distribution tails related to the
randomness in the MCMC fit (Robert, Casella, and Casella 2004),
generating a shift of probability mass towards the distribution centre
and stabilising it (i.e., decreasing variance without impacting bias).
On the other hand, just imposing robust uninformative priors against
extreme predictions would have decreased variance but also shifted the
distribution towards a non-decision zone, increasing bias (Hansen et al.
2000).\\
Since the number of model replications significantly impacts computation
times, we decided to use ten replicas, the lower value after which
showed performance stabilisation during the hyperparameter evaluation.\\
We also investigated whether bootstrapping between replications (Breiman
1996) would improve performance, but, contrary to theory (Díez-Pastor et
al. 2015), it was demonstrated to be slightly detrimental (Supplemental
Material S2) compared to simple ensembling.\\

@@

The field of literature review automation is maturing rapidly, and we
expect an increasing use of such technologies to manage the ever-faster
rate of scientific production. We believe it is appreciable that a
multiplicity of tools are being made available to let researchers and
policymakers find the instrument that better fits their needs.\\
We contribute to this field with an innovative framework that provide
excellent performance and easy integration with existing systematic
review pipelines. The value of this work lies not only in the framework
itself, which we provide as open-source software, but in the set of
methodologies we developed to solve various SRA issues and that can be
used to improve already existing solutions.\\
